Supporting Information

### 2022-03-16 Manuscript/Supplementary_Material/Indirect_direct_pollinators.Rmd
Update on ms and supporting info

#Bees
bees <- joined_tibble %>% filter(Node_FG=="Bee")
bees$ind_same_type_over_directed_int <- round(bees$ind_same_type_over_directed_int, digits = 1)
#Convert to factor
bees$position <- as.factor(bees$position)
bees$ind_same_type_over_directed_int <- as.factor(bees$ind_same_type_over_directed_int)
bee_plot <- ggplot(bees,aes(position,mean_natural_units))+
  geom_col(position = "dodge")+
  facet_grid(.~ind_same_type_over_directed_int,scale='free_x', space = "free_x") + ggtitle("Bees")+
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())+
  ylab("Frequency")+theme_bw() + xlab("")

#Coleoptera
cole <- joined_tibble %>% filter(Node_FG=="Coleoptera")
cole$ind_same_type_over_directed_int <- round(cole$ind_same_type_over_directed_int, digits = 1)
#Convert to factor
cole$position <- as.factor(cole$position)
cole$ind_same_type_over_directed_int <- as.factor(cole$ind_same_type_over_directed_int)
cole_plot <- ggplot(cole,aes(position,mean_natural_units))+
  geom_col(position = "dodge")+
  facet_grid(.~ind_same_type_over_directed_int,scale='free_x', space = "free_x") + ggtitle("Coleoptera")+
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())+
  ylab("Frequency")+theme_bw() + xlab("")

#Lepidoptera
lepi <- joined_tibble %>% filter(Node_FG=="Lepidoptera")
lepi$ind_same_type_over_directed_int <- round(lepi$ind_same_type_over_directed_int, digits = 1)
#Convert to factor
lepi$position <- as.factor(lepi$position)
lepi$ind_same_type_over_directed_int <- as.factor(lepi$ind_same_type_over_directed_int)
lepi_plot <- ggplot(lepi,aes(position,mean_natural_units))+
  geom_col(position = "dodge")+
  facet_grid(.~ind_same_type_over_directed_int,scale='free_x', space = "free_x") + ggtitle("Lepidoptera") +
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())+
  ylab("Frequency")+theme_bw()+ xlab("")

#Non-bee-Hymenoptera
non_bee <- joined_tibble %>% filter(Node_FG=="Non-bee-Hymenoptera")
non_bee$ind_same_type_over_directed_int <- round(non_bee$ind_same_type_over_directed_int, digits = 2)
#Convert to factor
non_bee$position <- as.factor(non_bee$position)
non_bee$ind_same_type_over_directed_int <- as.factor(non_bee$ind_same_type_over_directed_int)
non_bee_plot <- ggplot(non_bee,aes(position,mean_natural_units))+
  geom_col(position = "dodge")+
  facet_grid(.~ind_same_type_over_directed_int,scale='free_x', space = "free_x") + ggtitle("Non-bee-Hymenoptera") +
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())+
  ylab("Frequency")+theme_bw()+ xlab("")

#Non-syrphids-diptera
non_syr <- joined_tibble %>% filter(Node_FG=="Non-syrphids-diptera")
non_syr$ind_same_type_over_directed_int <- round(non_syr$ind_same_type_over_directed_int, digits = 1)
#Convert to factor
non_syr$position <- as.factor(non_syr$position)
non_syr$ind_same_type_over_directed_int <- as.factor(non_syr$ind_same_type_over_directed_int)
non_syr_plot <- ggplot(non_syr,aes(position,mean_natural_units))+
  geom_col(position = "dodge")+
  facet_grid(.~ind_same_type_over_directed_int,scale='free_x', space = "free_x") + ggtitle("Non-syrphids-diptera")+
theme(axis.title.x=element_blank(),
      axis.text.x=element_blank(),
      axis.ticks.x=element_blank())+
  ylab("Frequency")+theme_bw()+ xlab("")

#Syrphids
syr <- joined_tibble %>% filter(Node_FG=="Syrphids")
syr$ind_same_type_over_directed_int <- round(syr$ind_same_type_over_directed_int, digits = 1)
#Convert to factor
syr$position <- as.factor(syr$position)
syr$ind_same_type_over_directed_int <- as.factor(syr$ind_same_type_over_directed_int)
syr_plot <- ggplot(syr,aes(position,mean_natural_units))+
  geom_col(position = "dodge")+
  facet_grid(.~ind_same_type_over_directed_int,scale='free_x', space = "free_x") + ggtitle("Syrphids") +
   ylab("Frequency")+theme_bw() + xlab("Position within motif")

library(patchwork)
bee_plot / cole_plot / lepi_plot / non_bee_plot / non_syr_plot / syr_plot + plot_annotation(
  title = 'Proportion indirect/direct interactions (0, 0.3, 0.5, 1, 2, 3)',
  theme = theme(plot.title = element_text(size = 18, face="bold")))

>>>>

#Bees
bees <- joined_tibble %>% filter(Node_FG=="Bee")
bees$ind_same_type_over_directed_int <- round(bees$ind_same_type_over_directed_int, digits = 1)
#Convert to factor
bees$position <- as.factor(bees$position)
bees$indirect_interactions <- as.factor(bees$indirect_interactions)
bee_plot <- ggplot(bees,aes(position,mean_natural_units))+
  geom_col(position = "dodge")+
  facet_grid(.~indirect_interactions,scale='free_x', space = "free_x") + ggtitle("Bees")+
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())+
  ylab("Frequency")+theme_bw() + xlab("")

#Coleoptera
cole <- joined_tibble %>% filter(Node_FG=="Coleoptera")
cole$ind_same_type_over_directed_int <- round(cole$ind_same_type_over_directed_int, digits = 1)
#Convert to factor
cole$position <- as.factor(cole$position)
cole$indirect_interactions <- as.factor(cole$indirect_interactions)
cole_plot <- ggplot(cole,aes(position,mean_natural_units))+
  geom_col(position = "dodge")+
  facet_grid(.~indirect_interactions,scale='free_x', space = "free_x") + ggtitle("Coleoptera")+
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())+
  ylab("Frequency")+theme_bw() + xlab("")

#Lepidoptera
lepi <- joined_tibble %>% filter(Node_FG=="Lepidoptera")
lepi$ind_same_type_over_directed_int <- round(lepi$ind_same_type_over_directed_int, digits = 1)
#Convert to factor
lepi$position <- as.factor(lepi$position)
lepi$indirect_interactions <- as.factor(lepi$indirect_interactions)
lepi_plot <- ggplot(lepi,aes(position,mean_natural_units))+
  geom_col(position = "dodge")+
  facet_grid(.~indirect_interactions,scale='free_x', space = "free_x") + ggtitle("Lepidoptera") +
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())+
  ylab("Frequency")+theme_bw()+ xlab("")

#Non-bee-Hymenoptera
non_bee <- joined_tibble %>% filter(Node_FG=="Non-bee-Hymenoptera")
non_bee$ind_same_type_over_directed_int <- round(non_bee$ind_same_type_over_directed_int, digits = 2)
#Convert to factor
non_bee$position <- as.factor(non_bee$position)
non_bee$indirect_interactions <- as.factor(non_bee$indirect_interactions)
non_bee_plot <- ggplot(non_bee,aes(position,mean_natural_units))+
  geom_col(position = "dodge")+
  facet_grid(.~indirect_interactions,scale='free_x', space = "free_x") + ggtitle("Non-bee-Hymenoptera") +
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())+
  ylab("Frequency")+theme_bw()+ xlab("")

#Non-syrphids-diptera
non_syr <- joined_tibble %>% filter(Node_FG=="Non-syrphids-diptera")
non_syr$ind_same_type_over_directed_int <- round(non_syr$ind_same_type_over_directed_int, digits = 1)
#Convert to factor
non_syr$position <- as.factor(non_syr$position)
non_syr$indirect_interactions <- as.factor(non_syr$indirect_interactions)
non_syr_plot <- ggplot(non_syr,aes(position,mean_natural_units))+
  geom_col(position = "dodge")+
  facet_grid(.~indirect_interactions,scale='free_x', space = "free_x") + ggtitle("Non-syrphids-diptera")+
theme(axis.title.x=element_blank(),
      axis.text.x=element_blank(),
      axis.ticks.x=element_blank())+
  ylab("Frequency")+theme_bw()+ xlab("")

#Syrphids
syr <- joined_tibble %>% filter(Node_FG=="Syrphids")
syr$ind_same_type_over_directed_int <- round(syr$ind_same_type_over_directed_int, digits = 1)
#Convert to factor
syr$position <- as.factor(syr$position)
syr$indirect_interactions <- as.factor(syr$indirect_interactions)
syr_plot <- ggplot(syr,aes(position,mean_natural_units))+
  geom_col(position = "dodge")+
  facet_grid(.~indirect_interactions,scale='free_x', space = "free_x") + ggtitle("Syrphids") +
   ylab("Frequency")+theme_bw() + xlab("Position within motif")

library(patchwork)
bee_plot / cole_plot / lepi_plot / non_bee_plot / non_syr_plot / syr_plot + plot_annotation(
  title = 'Number of indirect interactions (0, 1, 2, 3)',
  theme = theme(plot.title = element_text(size = 18, face="bold")))

### 2022-03-16 Manuscript/Supplementary_Material/Supporting_information_Oikos.Rmd
Update on ms and supporting info

**Figure S6** Frequency of floral visitor groups and proportion of indirect-direct interactions.

**Figure S7** Frequency of plant groups per motif and proportion of indirect-direct interactions.

@@

```{r, echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE,out.width="90%",fig.align="center", fig.width=10,fig.height=12, fig.cap="\\textbf{Figure S6.} Frequency of the different floral visitor groups on the different motif positions aggregated by the proportion of indirect-direct interactions for the different motif positions."}

@@

#Bees
bees <- joined_tibble %>% filter(Node_FG=="Bee")
bees$ind_same_type_over_directed_int <- round(bees$ind_same_type_over_directed_int, digits = 1)
#Convert to factor
bees$position <- as.factor(bees$position)
bees$ind_same_type_over_directed_int <- as.factor(bees$ind_same_type_over_directed_int)
bee_plot <- ggplot(bees,aes(position,mean_natural_units))+
  geom_col(position = "dodge")+
  facet_grid(.~ind_same_type_over_directed_int,scale='free_x', space = "free_x") + ggtitle("Bees")+
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())+
  ylab("Frequency")+theme_bw() + xlab("")

#Coleoptera
cole <- joined_tibble %>% filter(Node_FG=="Coleoptera")
cole$ind_same_type_over_directed_int <- round(cole$ind_same_type_over_directed_int, digits = 1)
#Convert to factor
cole$position <- as.factor(cole$position)
cole$ind_same_type_over_directed_int <- as.factor(cole$ind_same_type_over_directed_int)
cole_plot <- ggplot(cole,aes(position,mean_natural_units))+
  geom_col(position = "dodge")+
  facet_grid(.~ind_same_type_over_directed_int,scale='free_x', space = "free_x") + ggtitle("Coleoptera")+
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())+
  ylab("Frequency")+theme_bw() + xlab("")

#Lepidoptera
lepi <- joined_tibble %>% filter(Node_FG=="Lepidoptera")
lepi$ind_same_type_over_directed_int <- round(lepi$ind_same_type_over_directed_int, digits = 1)
#Convert to factor
lepi$position <- as.factor(lepi$position)
lepi$ind_same_type_over_directed_int <- as.factor(lepi$ind_same_type_over_directed_int)
lepi_plot <- ggplot(lepi,aes(position,mean_natural_units))+
  geom_col(position = "dodge")+
  facet_grid(.~ind_same_type_over_directed_int,scale='free_x', space = "free_x") + ggtitle("Lepidoptera") +
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())+
  ylab("Frequency")+theme_bw()+ xlab("")

#Non-bee-Hymenoptera
non_bee <- joined_tibble %>% filter(Node_FG=="Non-bee-Hymenoptera")
non_bee$ind_same_type_over_directed_int <- round(non_bee$ind_same_type_over_directed_int, digits = 2)
#Convert to factor
non_bee$position <- as.factor(non_bee$position)
non_bee$ind_same_type_over_directed_int <- as.factor(non_bee$ind_same_type_over_directed_int)
non_bee_plot <- ggplot(non_bee,aes(position,mean_natural_units))+
  geom_col(position = "dodge")+
  facet_grid(.~ind_same_type_over_directed_int,scale='free_x', space = "free_x") + ggtitle("Non-bee-Hymenoptera") +
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())+
  ylab("Frequency")+theme_bw()+ xlab("")

#Non-syrphids-diptera
non_syr <- joined_tibble %>% filter(Node_FG=="Non-syrphids-diptera")
non_syr$ind_same_type_over_directed_int <- round(non_syr$ind_same_type_over_directed_int, digits = 1)
#Convert to factor
non_syr$position <- as.factor(non_syr$position)
non_syr$ind_same_type_over_directed_int <- as.factor(non_syr$ind_same_type_over_directed_int)
non_syr_plot <- ggplot(non_syr,aes(position,mean_natural_units))+
  geom_col(position = "dodge")+
  facet_grid(.~ind_same_type_over_directed_int,scale='free_x', space = "free_x") + ggtitle("Non-syrphids-diptera")+
theme(axis.title.x=element_blank(),
      axis.text.x=element_blank(),
      axis.ticks.x=element_blank())+
  ylab("Frequency")+theme_bw()+ xlab("")

#Syrphids
syr <- joined_tibble %>% filter(Node_FG=="Syrphids")
syr$ind_same_type_over_directed_int <- round(syr$ind_same_type_over_directed_int, digits = 1)
#Convert to factor
syr$position <- as.factor(syr$position)
syr$ind_same_type_over_directed_int <- as.factor(syr$ind_same_type_over_directed_int)
syr_plot <- ggplot(syr,aes(position,mean_natural_units))+
  geom_col(position = "dodge")+
  facet_grid(.~ind_same_type_over_directed_int,scale='free_x', space = "free_x") + ggtitle("Syrphids") +
   ylab("Frequency")+theme_bw() + xlab("Motif position")

library(patchwork)
bee_plot / cole_plot / lepi_plot / non_bee_plot / non_syr_plot / syr_plot + plot_annotation(title= 'Floral visitors',
  subtitle = 'Proportion indirect/direct interactions (0, 0.3, 0.5, 1, 2, 3)',
  theme = theme(plot.title = element_text(size = 18, face="bold"),plot.subtitle = element_text(size = 18, face="bold")))

@@

```{r, echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE,out.width="90%",fig.align="center", fig.width=10,fig.height=12, fig.cap="\\textbf{Figure S7.} Frequency of the different plant groups on the different motif positions aggregated by the proportion of indirect-direct interactions for the different motif positions."}

@@

#1 Selfing herbs
one <- joined_tibble %>% filter(Node_FG=="1")
one$ind_same_type_over_directed_int <- round(one$ind_same_type_over_directed_int, digits = 1)
#Convert to factor
one$position <- as.factor(one$position)
one$ind_same_type_over_directed_int <- as.factor(one$ind_same_type_over_directed_int)
one_plot <- ggplot(one,aes(position,mean_natural_units))+
  geom_col(position = "dodge")+
  facet_grid(.~ind_same_type_over_directed_int,scale='free_x', space = "free_x") + ggtitle("Selfing herbs")+
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())+
  ylab("Frequency")+ xlab("") + theme_bw()

#2 Small outcrossing perennials
two <- joined_tibble %>% filter(Node_FG=="2")
two$ind_same_type_over_directed_int <- round(two$ind_same_type_over_directed_int, digits = 1)
#Convert to factor
two$position <- as.factor(two$position)
two$ind_same_type_over_directed_int <- as.factor(two$ind_same_type_over_directed_int)
two_plot <- ggplot(two,aes(position,mean_natural_units))+
  geom_col(position = "dodge")+
  facet_grid(.~ind_same_type_over_directed_int,scale='free_x', space = "free_x") + ggtitle("Small outcrossing perennials")+
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())+
  ylab("Frequency")+ xlab("") + theme_bw()

#3 Self-incomp. perennials with large flowers
three <- joined_tibble %>% filter(Node_FG=="3")
three$ind_same_type_over_directed_int <- round(three$ind_same_type_over_directed_int, digits = 1)
#Convert to factor
three$position <- as.factor(three$position)
three$ind_same_type_over_directed_int <- as.factor(three$ind_same_type_over_directed_int)
three_plot <- ggplot(three,aes(position,mean_natural_units))+
  geom_col(position = "dodge")+
  facet_grid(.~ind_same_type_over_directed_int,scale='free_x', space = "free_x") + ggtitle("Self-incomp. perennials with large flowers") +
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())+
  ylab("Frequency")+ xlab("") + theme_bw()

#4 Tall plants with small unisexual flowers
four <- joined_tibble %>% filter(Node_FG=="4")
four$ind_same_type_over_directed_int <- round(four$ind_same_type_over_directed_int, digits = 2)
#Convert to factor
four$position <- as.factor(four$position)
four$ind_same_type_over_directed_int <- as.factor(four$ind_same_type_over_directed_int)
four_plot <- ggplot(four,aes(position,mean_natural_units))+
  geom_col(position = "dodge")+
  facet_grid(.~ind_same_type_over_directed_int,scale='free_x', space = "free_x") + ggtitle("Tall plants with small unisexual flowers") +
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())+
  ylab("Frequency")+ xlab("") + theme_bw()

#5 Short-lived outcrossers with long zygomorphic flowers
five <- joined_tibble %>% filter(Node_FG=="5")
five$ind_same_type_over_directed_int <- round(five$ind_same_type_over_directed_int, digits = 1)
#Convert to factor
five$position <- as.factor(five$position)
five$ind_same_type_over_directed_int <- as.factor(five$ind_same_type_over_directed_int)
five_plot <- ggplot(five,aes(position,mean_natural_units))+
  geom_col(position = "dodge")+
  facet_grid(.~ind_same_type_over_directed_int,scale='free_x', space = "free_x") + ggtitle("Short-lived outcrossers with long zygomorphic flowers")+
  ylab("Frequency") + xlab("Motif position") + theme_bw()

library(patchwork)
one_plot / two_plot / three_plot / four_plot / five_plot + plot_annotation(title= 'Plants', subtitle = 'Proportion indirect/direct interactions (0, 0.3, 0.5, 1, 2, 3)',
  theme = theme(plot.title = element_text(size = 18, face="bold"),plot.subtitle = element_text(size = 18, face="bold")))

>>>>

**Figure S6** Frequency of floral visitor groups and number of indirect interactions per motif positions.

**Figure S7** Frequency of plant groups and number of indirect interactions per motif positions.

@@

```{r, echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE,out.width="90%",fig.align="center", fig.width=10,fig.height=12, fig.cap="\\textbf{Figure S6.} Frequency of the different floral visitor groups on the different motif positions aggregated by the number of indirect interactions for the different motif positions."}

@@

#Bees
bees <- joined_tibble %>% filter(Node_FG=="Bee")
bees$ind_same_type_over_directed_int <- round(bees$ind_same_type_over_directed_int, digits = 1)
#Convert to factor
bees$position <- as.factor(bees$position)
bees$indirect_interactions <- as.factor(bees$indirect_interactions)
bee_plot <- ggplot(bees,aes(position,mean_natural_units))+
  geom_col(position = "dodge")+
  facet_grid(.~indirect_interactions,scale='free_x', space = "free_x") + ggtitle("Bees")+
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())+
  ylab("Frequency")+theme_bw() + xlab("")

#Coleoptera
cole <- joined_tibble %>% filter(Node_FG=="Coleoptera")
cole$ind_same_type_over_directed_int <- round(cole$ind_same_type_over_directed_int, digits = 1)
#Convert to factor
cole$position <- as.factor(cole$position)
cole$indirect_interactions <- as.factor(cole$indirect_interactions)
cole_plot <- ggplot(cole,aes(position,mean_natural_units))+
  geom_col(position = "dodge")+
  facet_grid(.~indirect_interactions,scale='free_x', space = "free_x") + ggtitle("Coleoptera")+
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())+
  ylab("Frequency")+theme_bw() + xlab("")

#Lepidoptera
lepi <- joined_tibble %>% filter(Node_FG=="Lepidoptera")
lepi$ind_same_type_over_directed_int <- round(lepi$ind_same_type_over_directed_int, digits = 1)
#Convert to factor
lepi$position <- as.factor(lepi$position)
lepi$indirect_interactions <- as.factor(lepi$indirect_interactions)
lepi_plot <- ggplot(lepi,aes(position,mean_natural_units))+
  geom_col(position = "dodge")+
  facet_grid(.~indirect_interactions,scale='free_x', space = "free_x") + ggtitle("Lepidoptera") +
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())+
  ylab("Frequency")+theme_bw()+ xlab("")

#Non-bee-Hymenoptera
non_bee <- joined_tibble %>% filter(Node_FG=="Non-bee-Hymenoptera")
non_bee$ind_same_type_over_directed_int <- round(non_bee$ind_same_type_over_directed_int, digits = 2)
#Convert to factor
non_bee$position <- as.factor(non_bee$position)
non_bee$indirect_interactions <- as.factor(non_bee$indirect_interactions)
non_bee_plot <- ggplot(non_bee,aes(position,mean_natural_units))+
  geom_col(position = "dodge")+
  facet_grid(.~indirect_interactions,scale='free_x', space = "free_x") + ggtitle("Non-bee-Hymenoptera") +
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())+
  ylab("Frequency")+theme_bw()+ xlab("")

#Non-syrphids-diptera
non_syr <- joined_tibble %>% filter(Node_FG=="Non-syrphids-diptera")
non_syr$ind_same_type_over_directed_int <- round(non_syr$ind_same_type_over_directed_int, digits = 1)
#Convert to factor
non_syr$position <- as.factor(non_syr$position)
non_syr$indirect_interactions <- as.factor(non_syr$indirect_interactions)
non_syr_plot <- ggplot(non_syr,aes(position,mean_natural_units))+
  geom_col(position = "dodge")+
  facet_grid(.~indirect_interactions,scale='free_x', space = "free_x") + ggtitle("Non-syrphids-diptera")+
theme(axis.title.x=element_blank(),
      axis.text.x=element_blank(),
      axis.ticks.x=element_blank())+
  ylab("Frequency")+theme_bw()+ xlab("")

#Syrphids
syr <- joined_tibble %>% filter(Node_FG=="Syrphids")
syr$ind_same_type_over_directed_int <- round(syr$ind_same_type_over_directed_int, digits = 1)
#Convert to factor
syr$position <- as.factor(syr$position)
syr$indirect_interactions <- as.factor(syr$indirect_interactions)
syr_plot <- ggplot(syr,aes(position,mean_natural_units))+
  geom_col(position = "dodge")+
  facet_grid(.~indirect_interactions,scale='free_x', space = "free_x") + ggtitle("Syrphids") +
   ylab("Frequency")+theme_bw() + xlab("Motif position")

library(patchwork)
bee_plot / cole_plot / lepi_plot / non_bee_plot / non_syr_plot / syr_plot + plot_annotation(title= 'Floral visitors',
  subtitle = 'Number of indirect interactions (0, 1, 2, 3)',
  theme = theme(plot.title = element_text(size = 18, face="bold"),plot.subtitle = element_text(size = 18, face="bold")))

@@

```{r, echo=FALSE, message=FALSE, cache=FALSE, warning=FALSE,out.width="90%",fig.align="center", fig.width=10,fig.height=12, fig.cap="\\textbf{Figure S7.} Frequency of the different plant groups on the different motif positions aggregated by the number of indirect interactions for the different motif positions."}

@@

#1 Selfing herbs
one <- joined_tibble %>% filter(Node_FG=="1")
one$ind_same_type_over_directed_int <- round(one$ind_same_type_over_directed_int, digits = 1)
#Convert to factor
one$position <- as.factor(one$position)
one$indirect_interactions <- as.factor(one$indirect_interactions)
one_plot <- ggplot(one,aes(position,mean_natural_units))+
  geom_col(position = "dodge")+
  facet_grid(.~indirect_interactions,scale='free_x', space = "free_x") + ggtitle("Selfing herbs")+
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())+
  ylab("Frequency")+ xlab("") + theme_bw()

#2 Small outcrossing perennials
two <- joined_tibble %>% filter(Node_FG=="2")
two$ind_same_type_over_directed_int <- round(two$ind_same_type_over_directed_int, digits = 1)
#Convert to factor
two$position <- as.factor(two$position)
two$indirect_interactions <- as.factor(two$indirect_interactions)
two_plot <- ggplot(two,aes(position,mean_natural_units))+
  geom_col(position = "dodge")+
  facet_grid(.~indirect_interactions,scale='free_x', space = "free_x") + ggtitle("Small outcrossing perennials")+
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())+
  ylab("Frequency")+ xlab("") + theme_bw()

#3 Self-incomp. perennials with large flowers
three <- joined_tibble %>% filter(Node_FG=="3")
three$ind_same_type_over_directed_int <- round(three$ind_same_type_over_directed_int, digits = 1)
#Convert to factor
three$position <- as.factor(three$position)
three$indirect_interactions <- as.factor(three$indirect_interactions)
three_plot <- ggplot(three,aes(position,mean_natural_units))+
  geom_col(position = "dodge")+
  facet_grid(.~indirect_interactions,scale='free_x', space = "free_x") + ggtitle("Self-incomp. perennials with large flowers") +
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())+
  ylab("Frequency")+ xlab("") + theme_bw()

#4 Tall plants with small unisexual flowers
four <- joined_tibble %>% filter(Node_FG=="4")
four$ind_same_type_over_directed_int <- round(four$ind_same_type_over_directed_int, digits = 2)
#Convert to factor
four$position <- as.factor(four$position)
four$indirect_interactions <- as.factor(four$indirect_interactions)
four_plot <- ggplot(four,aes(position,mean_natural_units))+
  geom_col(position = "dodge")+
  facet_grid(.~indirect_interactions,scale='free_x', space = "free_x") + ggtitle("Tall plants with small unisexual flowers") +
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())+
  ylab("Frequency")+ xlab("") + theme_bw()

#5 Short-lived outcrossers with long zygomorphic flowers
five <- joined_tibble %>% filter(Node_FG=="5")
five$ind_same_type_over_directed_int <- round(five$ind_same_type_over_directed_int, digits = 1)
#Convert to factor
five$position <- as.factor(five$position)
five$indirect_interactions <- as.factor(five$indirect_interactions)
five_plot <- ggplot(five,aes(position,mean_natural_units))+
  geom_col(position = "dodge")+
  facet_grid(.~indirect_interactions,scale='free_x', space = "free_x") + ggtitle("Short-lived outcrossers with long zygomorphic flowers")+
  ylab("Frequency") + xlab("Motif position") + theme_bw()

library(patchwork)
one_plot / two_plot / three_plot / four_plot / five_plot + plot_annotation(title= 'Plants', subtitle = 'Number of indirect interactions (0, 1, 2, 3)',
  theme = theme(plot.title = element_text(size = 18, face="bold"),plot.subtitle = element_text(size = 18, face="bold")))
